### 2020-03-12 README.Rmd
Problem with readme at chunk 19

bw_predict %>%
  ggplot(aes(growth, growth_hat)) +
  geom_point() +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0)
```

>>>>

bw_predict %>%
  group_by(focal_ID) %>%
  summarise(growth = mean(growth), growth_hat = mean(growth_hat)) %>%
  ggplot(aes(growth, growth_hat)) +
  geom_point(size = 0.5, color = rgb(0,0,0,0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0)
```
